---
title: "Diseases monitoring"
author: "ReliefWeb"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: pdf_document
always_allow_html: true
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding) })
---

```{r setup, include=FALSE}
library("rvest")
library(tabulizer)
library(dplyr)
library(miniUI)
library(tidyverse)
library(pdftools)

library(xlsx)
library(condformat)
library("readxl")
library(tidyr)
library(tidyverse)
library(DT)
library(reshape2)
library("ggplot2")
```

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```

### Green: Below 25% of the average of that month
### Yellow: On the average of that month
### Red: Above 25% of the average of that month




\pagebreak
### Dengue

**Dengue cases in Nepal:**

```{r sourcing data processing scripts, include=FALSE,echo=FALSE}
source("Web scrapping and data cleaning.R")

```


```{r Dengue_Nepal, fig.width=7, fig.height=3, echo=FALSE}
save_data <- readRDS(file = "save_data_nepal_dengue.Rdata")

my_data <- save_data
my_data <- transform(my_data, `2020` = as.numeric(`2020`))
my_data <- my_data %>% rename("2017" =  "X2017", "2018" =  "X2018", "2019" =  "X2019", "2020" =  "X2020")

my_data$seventen_mean <- ifelse(my_data$`2017` > means$Above, 2,
                                ifelse(my_data$`2017` < means$Below, 0,
                                       1))
my_data$eigthten_mean <- ifelse(my_data$`2018` > means$Above, 2,
                                ifelse(my_data$`2018` < means$Below, 0,
                                       1))
my_data$nineten_mean <- ifelse(my_data$`2019` > means$Above, 2,
                               ifelse(my_data$`2019` < means$Below, 0,
                                      1))
my_data$twente_mean <- ifelse(my_data$`2020` > means$Above, 2,
                              ifelse(my_data$`2020` < means$Below, 0,
                                     1))


DT::datatable(
  my_data,
  rownames = FALSE,
  options = list(pageLength = 15,
                 columnDefs = list(list(targets = c(5:8), visible = FALSE))
  )
) %>% 
   formatStyle(columns = "2017",
              valueColumns = "seventen_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>%
  formatStyle(columns = "2018",
              valueColumns = "eigthten_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>%
  formatStyle(columns = "2019",
              valueColumns = "nineten_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>%
  formatStyle(columns = "2020",
              valueColumns = "twente_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00")))

save_data$Month <-factor(save_data$Month, 
                         levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun",
                                    "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))

meltdf <- melt(save_data,id="Month")
ggplot(meltdf,aes(x=Month,y=value,colour=variable,group=variable)) + geom_line()


```

Source: Government of Nepal, Ministry of Health and Population, Department of Health Services, Epidemiology and Disease Control Division

\pagebreak

**Dengue cases in Sri Lanka:**

```{r Dengue_Srilanka, fig.width=7, fig.height=3, echo=FALSE}
#readRDS data from processing files
my_data <- readRDS(file = "sri_lanka_dengue.Rdata")

DT::datatable(
  my_data,
  rownames = FALSE,
  options = list(pageLength = 15,
                 columnDefs = list(list(targets = c(12:22), visible = FALSE))
  )
) %>% 
  formatStyle(columns = "2010",
              valueColumns = "ten_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>% 
  formatStyle(columns = "2011",
              valueColumns = "eleven_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>% 
  
  formatStyle(columns = "2012",
              valueColumns = "twelve_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>%
  
  formatStyle(columns = "2013",
              valueColumns = "thirdten_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>%
  formatStyle(columns = "2014",
              valueColumns = "fourthten_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>%
  formatStyle(columns = "2015",
              valueColumns = "fiveten_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>%
  formatStyle(columns = "2016",
              valueColumns = "sixten_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>%
  formatStyle(columns = "2017",
              valueColumns = "seventen_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>%
  formatStyle(columns = "2018",
              valueColumns = "eigthten_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>%
  formatStyle(columns = "2019",
              valueColumns = "nineten_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>%
  formatStyle(columns = "2020",
              valueColumns = "twente_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00")))

#readRDS ggplot data from web scrapping and data cleaning file
save_data <- readRDS(file = "sri_lanka_dengue_ggplot.Rdata")
save_data$Month <-factor(save_data$Month, 
                         levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun",
                                    "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))

meltdf <- melt(save_data,id="Month")
ggplot(meltdf,aes(x=Month,y=value,colour=variable,group=variable)) + geom_line()





```

Source: Epidemiology Unit of Ministry of Health of Sri Lanka

\pagebreak


**Dengue cases in Fiji:**

```{r Dengue_Fiji, fig.width=7, fig.height=3, echo=FALSE}
#readRDS processed data from sourced file
my_data<- readRDS(file = "save_data_fiji_dengue.Rdata")

DT::datatable(
  my_data,
  rownames = FALSE,
  options = list(pageLength = 15,
                 columnDefs = list(list(targets = c(4:6), visible = FALSE))
  )
) %>% 
  formatStyle(columns = "2018",
              valueColumns = "eigthten_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>%
  formatStyle(columns = "2019",
              valueColumns = "nineten_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>%
  formatStyle(columns = "2020",
              valueColumns = "twente_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00")))

#readRDS processed data for ggplot graph
save_data<- readRDS(file = "save_data_fiji_dengue_ggplot.Rdata")


save_data$Month <-factor(save_data$Month, 
                         levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun",
                                    "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))

meltdf <- melt(save_data,id="Month")
ggplot(meltdf,aes(x=Month,y=value,colour=variable,group=variable)) + geom_line()



```

Source: Pacific Syndromic Surveillance System Weekly Bulletin - WHO

\pagebreak


**Dengue cases in French Polynesia:**

```{r Dengue_French_Polynesia, fig.width=7, fig.height=3, echo=FALSE}

#readRDS processed data from sourced file
my_data<- readRDS(file = "french_polynesia_dengue.Rdata")

DT::datatable(
  my_data,
  rownames = FALSE,
  options = list(pageLength = 15,
                 columnDefs = list(list(targets = c(4:6), visible = FALSE))
  )
) %>% 
  formatStyle(columns = "2018",
              valueColumns = "eigthten_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>%
  formatStyle(columns = "2019",
              valueColumns = "nineten_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>%
  formatStyle(columns = "2020",
              valueColumns = "twente_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00")))

#readRDS processed data for ggplot graph
save_data<- readRDS(file = "french_polynesia_dengue_ggplot.Rdata")

save_data$Month <-factor(save_data$Month, 
                         levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun",
                                    "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))

meltdf <- melt(save_data,id="Month")
ggplot(meltdf,aes(x=Month,y=value,colour=variable,group=variable)) + geom_line()


```
Source: Pacific Syndromic Surveillance System Weekly Bulletin - WHO

\pagebreak


**Dengue cases in Marshall Islands:**

```{r Dengue_Marshall_Islands, fig.width=7, fig.height=3, echo=FALSE}
#readRDS processed data from sourced file
my_data<- readRDS(file = "marshall_dengue.Rdata")

DT::datatable(
  my_data,
  rownames = FALSE,
  options = list(pageLength = 15,
                 columnDefs = list(list(targets = c(4:6), visible = FALSE))
  )
) %>% 
  formatStyle(columns = "2018",
              valueColumns = "eigthten_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>%
  formatStyle(columns = "2019",
              valueColumns = "nineten_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>%
  formatStyle(columns = "2020",
              valueColumns = "twente_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00")))

#readRDS processed data for ggplot graph
save_data<- readRDS(file = "marshall_dengue_ggplot.Rdata")
save_data$Month <-factor(save_data$Month, 
                         levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun",
                                    "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))

meltdf <- melt(save_data,id="Month")
ggplot(meltdf,aes(x=Month,y=value,colour=variable,group=variable)) + geom_line()



```
Source: Pacific Syndromic Surveillance System Weekly Bulletin - WHO
\pagebreak


**Dengue cases in Malaysia:**

```{r Dengue_Malaysia, fig.width=7, fig.height=3, echo=FALSE}
#readRDS processed data from sourced file
my_data<- readRDS(file = "Malaysia_dengue.Rdata")


DT::datatable(
  my_data,
  rownames = FALSE,
  options = list(pageLength = 15,
                 columnDefs = list(list(targets = c(6:10), visible = FALSE))
  )
) %>% 
  formatStyle(columns = "2016",
              valueColumns = "sixten_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>%
  formatStyle(columns = "2017",
              valueColumns = "seventen_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>%
  formatStyle(columns = "2018",
              valueColumns = "eigthten_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>%
  formatStyle(columns = "2019",
              valueColumns = "nineten_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>%
  formatStyle(columns = "2020",
              valueColumns = "twente_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00")))
#readRDS processed data for ggplot graph
save_data<- readRDS(file = "Malaysia_dengue_ggplot.Rdata")

save_data$Month <-factor(save_data$Month, 
                         levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun",
                                    "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))

meltdf <- melt(save_data,id="Month")
ggplot(meltdf,aes(x=Month,y=value,colour=variable,group=variable)) + geom_line()



```
Source: iDengue untuk komuniti - The Government of Malaysia
\pagebreak

### Polio

**Polio cases in Afghanistan**

```{r Polio_Afghanistan, fig.width=7, fig.height=3, echo=FALSE}

#readRDS processed data from sourced file
my_data<- readRDS(file = "afghanistan_polio.Rdata")


DT::datatable(
  my_data,
  rownames = FALSE,
  options = list(pageLength = 15,
                 columnDefs = list(list(targets = c(7:12), visible = FALSE))
  )
) %>% 
  formatStyle(columns = "2015",
              valueColumns = "fiveten_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>%
  formatStyle(columns = "2016",
              valueColumns = "sixten_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>%
  formatStyle(columns = "2017",
              valueColumns = "seventen_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>%
  formatStyle(columns = "2018",
              valueColumns = "eigthten_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>%
  formatStyle(columns = "2019",
              valueColumns = "nineten_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>%
  formatStyle(columns = "2020",
              valueColumns = "twente_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00")))

#readRDS processed data for ggplot graph
save_data<- readRDS(file = "afghanistan_polio_ggplot.Rdata")

save_data$Month <-factor(save_data$Month, 
                         levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun",
                                    "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))

meltdf <- melt(save_data,id="Month")
ggplot(meltdf,aes(x=Month,y=value,colour=variable,group=variable)) + geom_line()


```
Source: Polio Global Eradication Initiative

\pagebreak


**Polio cases in Pakistan**

```{r Polio_Pakistan, fig.width=7, fig.height=3, echo=FALSE}

#readRDS processed data from sourced file
my_data<- readRDS(file = "pakistan_polio.Rdata")

DT::datatable(
  my_data,
  rownames = FALSE,
  options = list(pageLength = 15,
                 columnDefs = list(list(targets = c(7:12), visible = FALSE))
  )
) %>% 
  formatStyle(columns = "2015",
              valueColumns = "fiveten_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>%
  formatStyle(columns = "2016",
              valueColumns = "sixten_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>%
  formatStyle(columns = "2017",
              valueColumns = "seventen_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>%
  formatStyle(columns = "2018",
              valueColumns = "eigthten_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>%
  formatStyle(columns = "2019",
              valueColumns = "nineten_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>%
  formatStyle(columns = "2020",
              valueColumns = "twente_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00")))

#readRDS processed data for ggplot graph
save_data<- readRDS(file = "pakistan_polio_ggplot.Rdata")

save_data$Month <-factor(save_data$Month, 
                         levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun",
                                    "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))

meltdf <- melt(save_data,id="Month")
ggplot(meltdf,aes(x=Month,y=value,colour=variable,group=variable)) + geom_line()


```
Source: Polio Global Eradication Initiative
\pagebreak

### Measles

**Measles cases in Bangladesh**

```{r Measles_Bangladesh, fig.width=7, fig.height=3, echo=FALSE}

#readRDS processed data from sourced file
my_data<- readRDS(file = "Bangladesh_Measles.Rdata")

DT::datatable(
  my_data,
  rownames = FALSE,
  options = list(pageLength = 15,
                 columnDefs = list(list(targets = c(4:6), visible = FALSE))
  )
) %>% 
  formatStyle(columns = "2018",
              valueColumns = "eigthten_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>%
  formatStyle(columns = "2019",
              valueColumns = "nineten_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>%
  formatStyle(columns = "2020",
              valueColumns = "twente_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00")))

#readRDS processed data for ggplot graph
save_data<- readRDS(file = "Bangladesh_Measles_ggplot.Rdata")

save_data$Month <-factor(save_data$Month, 
                         levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun",
                                    "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))

meltdf <- melt(save_data,id="Month")
ggplot(meltdf,aes(x=Month,y=value,colour=variable,group=variable)) + geom_line()



```
Source: Epidemiological Highlights - WHO
\pagebreak

### Diarrhea

**Diarrhea cases in Bangladesh**

```{r Diarrhea_Bangladesh, fig.width=7, fig.height=3, echo=FALSE}

#readRDS processed data from sourced file
my_data<- readRDS(file = "Bangladesh_Diarrhea.Rdata")


DT::datatable(
  my_data,
  rownames = FALSE,
  options = list(pageLength = 15,
                 columnDefs = list(list(targets = c(4:6), visible = FALSE))
  )
) %>% 
  formatStyle(columns = "2018",
              valueColumns = "eigthten_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>%
  formatStyle(columns = "2019",
              valueColumns = "nineten_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00"))) %>%
  formatStyle(columns = "2020",
              valueColumns = "twente_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00")))

#readRDS processed data for ggplot graph
save_data<- readRDS(file = "Bangladesh_Diarrhea_ggplot.Rdata")

save_data$Month <-factor(save_data$Month, 
                         levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun",
                                    "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))

meltdf <- melt(save_data,id="Month")
ggplot(meltdf,aes(x=Month,y=value,colour=variable,group=variable)) + geom_line()


```
Source: Epidemiological Highlights - WHO
\pagebreak



### Drought

**Drought Situation Report- Sri Lanka**

Source: Disaster Management Centre for Safer Communities & Sustainable Development in Sri Lanka

```{r Drought_SriLanka, fig.width=7, fig.height=3,  echo=FALSE}


#readRDS processed data from sourced file
my_data<- readRDS(file = "save_data_srilanka_drought.Rdata")

DT::datatable(
  my_data,
  rownames = FALSE,
  options = list(pageLength = 52,
                 columnDefs = list(list(targets = 3, visible = FALSE))
  )
)  %>%
  formatStyle(columns = "2020",
              valueColumns = "twente_mean",
              backgroundColor = styleEqual(levels = c(0,1,2), values = c("#008000","#FFA500","#F00")))




```


```{r temp files, echo=FALSE}
unlink(paste0(normalizePath(tempdir()), "/", dir(tempdir())), recursive = TRUE)

```
